Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-07-06 paper/paper-nature-revised.tex

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Digitization of the Australian Parliamentary Debates, 1998-2022},
  pdfauthor={Lindsay Katz; Rohan Alexander},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{July 5, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced, breakable, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, formally known as
Hansard, plays a fundamental role in capturing the history of political
proceedings and facilitating the exploration of valuable research
questions. Originating in the British parliament, the production of
Hansard became tradition in many other Commonwealth countries, such as
Canada and Australia\textsuperscript{1}. Given the content and magnitude
of these records, they have significance, particularly in the context of
political science research. In the case of Canada, the Hansard has been
digitized for 1901 to 2019\textsuperscript{2}. Having a digitized
version of Hansard enables researchers to conduct text analysis and
statistical modelling. Following the lead of that project, in this paper
we introduce a similar database for Australia. This is composed of
individual datasets for each sitting day in the House of Representatives
from 1998 to 2022, containing details on everything said in parliament
in a form that can be readily used by researchers. With the development
of tools for large-scale text analysis, this database will serve as a
resource for understanding political behaviour in Australia over time.

The Australian House of Representatives `the House' performs a number of
crucial governmental functions, such as creating new laws and overseeing
government expenditure\textsuperscript{3, ch.~1}. Politicians in the
House are referred to as Members of Parliament (MPs). The House operates
under a parallel chamber setup, meaning there are two debate venues
where proceedings take place: the Chamber, and the Federation Chamber.
Sittings of the House follow a predefined order of business, regulated
by procedural rules called standing orders\textsuperscript{3, ch.~8}. A
typical sitting day in the Chamber has a number of scheduled proceedings
including debates on government business, 90 second member statements,
and Question Time\textsuperscript{3, ch.~8}. The Federation Chamber was
created in 1994 as a subordinate debate venue of the Chamber. This
allows for better time management of House business as its proceedings
occur simultaneously with those of the Chamber\textsuperscript{3,
ch.~21}. Sittings in the Federation Chamber are different to those of
the Chamber in terms of their order of business and scope of discussion.
Business matters discussed in the Federation Chamber are limited largely
to intermediate stages of bill development, and the business of private
Members\textsuperscript{3, ch.~21}. It is the recording and compilation
of these proceedings on which Hansard is based, and it is essentially,
but not entirely, verbatim.

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not accessible for large scale analysis. To this
point, various researchers have had to create their own databases of
usable, complete data based on content from the Australian Parliament
website. For instance,\textsuperscript{4} created an online, easy to
read database of Hansard from 1901 to 1980 using the XML files. These
data can be navigated by year, parliament, people, and
bills\textsuperscript{4}. To make the Australian Parliamentary Handbook
more accessible,\textsuperscript{5} has released an \texttt{R} package
which includes data on all MPs from 1945 to 2019.
Further,\textsuperscript{6} created the \texttt{AustralianPoliticians}
\texttt{R} package, which contains several datasets related to the
political and biographical information of Australian federal politicians
who were active between 1901 and 2021.

Many papers exist which use components of Australian Hansard to explore
various research topics. For example,\textsuperscript{7} used the
Hansard to investigate occurrences of unparliamentary comments by MPs,
where the Speaker tells that MP to withdraw their
remark.\textsuperscript{8} worked with Question Time data from Hansard
transcripts during February and March of 2003, to investigate resistance
of politicians in answering questions about Iraq.\textsuperscript{9} use
Hansard to quantify political prominence by investigating strategic
mentions of interest groups by elected officials.
Finally,\textsuperscript{10} construct a dataset of the Australian
Hansard, along with an analysis of the effect of elections and changes
in Prime Ministers upon topics mentioned in
parliament.\textsuperscript{10} created this database with the static
PDF versions of Hansard, using OCR to digitize these files into text
which is suitable for analysis. This means there are considerable
digitization errors especially in the first half of the dataset.

@@

The approach to parsing contents of an XML document depends on its tree
structure. As such, to create this database, we started by looking at a
single Hansard XML transcript from 2019. Doing so enabled us to identify
the various components of interest in the document, and how each one can
be parsed according to its corresponding structural form. Parsing was
performed in \texttt{R} using the \texttt{XML} and \texttt{xml2}
packages\textsuperscript{11,12}. Focusing on one transcript also allowed
us to ensure that all key components of the transcript were parsed and
captured in as much detail as possible. The typical form of a Hansard
XML transcript is summarized in the nested list below. This provides an
overview, but does not contain every possible nested element that may be
found in a Hansard XML.

@@

The next step was to further develop our script to produce tidy data
sets, as defined and introduced by\textsuperscript{13}. These contain
all parsed text elements, where each statement is separated onto its own
row with details about the MP who is speaking, and rows are maintained
in chronological order. This first involved correcting the variable
classes and adding several indicator variables to differentiate where
statements came from, such as Chamber versus Federation Chamber or
\texttt{\textless{}subdebate.1\textgreater{}} versus
\texttt{\textless{}subdebate.2\textgreater{}}. The next key task stemmed
from the fact that the raw text data were not separated by each
statement when parsed. In other words, any interjections, comments made
by the Speaker or Deputy Speaker and continuations within an individual
speech were all parsed together as a single string. As such, the name,
name ID, electorate and party details were only provided for the person
whose turn it was to speak. There were many intricacies in the task of
splitting these speeches in a way that would be generalizable across
sitting days. Details on these are provided in
Section~\ref{sec-interject}.

@@

The need for a second script stems from the fact that when established
in 1994, the Federation Chamber was originally named the Main Committee.
The Main Committee was renamed to the Federation Chamber in
mid-2012\textsuperscript{3, ch.~21}. As a result, the child node under
which Federation Chamber proceedings are nested is named
\texttt{\textless{}maincomm.xscript\textgreater{}} in all XML files
prior to 14 August 2012. Having developed our first script based on
Hansard from recent years, all XPath expressions contain the
\texttt{\textless{}fedchamb.xscript\textgreater{}} specification. To
avoid causing issues in our first script which successfully parses about
10 years of Hansard, we created a second script where we replaced all
occurrences of \texttt{\textless{}fedchamb.xscript\textgreater{}} with
\texttt{\textless{}maincomm.xscript\textgreater{}}. After making this
modification and accounting for other small changes such as time stamp
formatting, this second script successfully parses all Hansard sitting
days from 10 May 2011 to 28 June 2012 (inclusive).

@@

A key characteristic of the Australian parliamentary system is the
ability for the executive government to be held accountable for their
decisions. One core mechanism by which this is achieved is called
Question Time. This is a period of each sitting day in the Chamber where
MPs can ask ministers two types of questions: questions in writing which
are written in advance, or questions without notice which are asked
verbally in the Chamber and are responded to in real
time\textsuperscript{14}. Questions without notice are included directly
in the \texttt{"chamber.xscript"} child node, with sub-child nodes
called \texttt{"question"} and \texttt{"answer"} to differentiate the
two. Questions in writing, however, are embedded in their own child node
called \texttt{"answers.to.questions"} at the end of the XML file.

@@

We then added an order variable to the dataset based on row number, to
keep track of the order in which everything was said. The next step was
to fill the name, name ID, electorate and party variables with the
correct data for each row. We also wanted to add the gender and unique
identifier for each individual as found in the
\texttt{AustralianPoliticians} package. To do so, we created a lookup
table, which contained the unique incomplete form in which the name was
transcribed, and the corresponding full name, name ID, electorate,
party, gender, and unique ID for that individual.
Figure~\ref{fig-lookup} provides an example of this. We used the main
dataset from the \texttt{AustralianPoliticians} package in the creation
of each lookup table\textsuperscript{6}.

@@

\textbf{Another fundamental component of parliamentary proceedings is
voting. In the House, when a question arises such as ``The question is
that the amendment be agreed to'', Members are asked to cast their vote
either in the affirmative or in the negative, and the majority of votes
as judged by the Speaker determines the outcome\textsuperscript{3}.
Further, Members can vote in an unofficial arrangement called pairs, in
which as written in Chapter 8 of\textsuperscript{3}, ``can be used to
enable a Member on one side of the House to be absent for any votes when
a Member from the other side is to be absent at the same time or when,
by agreement, a Member abstains from voting''. If the result as
determined by the Speaker is challenged by more than one MP, this leads
to a division of the House in which the question is re-stated and
Members must move to the left or right of their chair depending on how
they vote, so that the votes can be re-counted and
recorded\textsuperscript{3}.}

@@

Our database is available in both CSV and parquet formats. It covers all
sitting days of the House of Representatives from 02 March 1998 to 08
September 2022 \textbf{where an XML transcript is available}, so there
are \textbf{1,532 individual sitting day} files for each format.
\textbf{Additionally, there is a single corpus file in both CSV and
Parquet forms containing the data from all sitting days, with a date
variable added to allow for distinction and filtering of individual
sitting days. There is also a CSV and Parquet file containing all parsed
debate topics.} All data records are available on the general-purpose
repository Zenodo, at
https://doi.org/10.5281/zenodo.7799678\textsuperscript{15}. For each
\textbf{Hansard data} file, \textbf{that is, the corpus and the
individual sitting day files}, each row contains an individual
statement, with details on the individual speaking. For general
statements transcribed as made by ``Honourable members'' for example,
these variables cannot be specified. Table~\ref{tbl-vars} provides an
overview of each variable found in the \textbf{Hansard data files in
the} database.

@@

{\centering \includegraphics[width=4.58333in,height=\textheight]{n_daily_speeches.png}

@@

\textbf{Next, we explored the number of unique names detected on each
sitting day disaggregated by debate venue, visualized in
Figure~\ref{fig-names}. As expected, there are generally more individual
MPs detected to be present in the Chamber proceedings in our data than
in the Federation Chamber proceedings. Further, in both venues, the
number of individuals detected per sitting day appears to have increased
since around 2008-2009, with a maximum of 116 and 87 unique names
detected for the Chamber and Federation Chamber, respectively. Across
the time frame of our data, there was a daily average of 84 unique names
detected in the Chamber, and 34 in the Federation Chamber. These
observations are in accordance with the official number of Members
belonging to the House of Representatives, which was 148 in 1998, 150 in
2001, and then increased to 151 in the 2019 general
election\textsuperscript{3}.}

@@

{\centering \includegraphics[width=4.58333in,height=\textheight]{n_unique_names.png}

@@

\textbf{We then computed the total number of speeches made in our
database by political party, summarized in
Table~\ref{tbl-speeches_by_party}. We found that the Australian Labor
Party made the most speeches overall, followed by the Liberal Party of
Australia, and the Nationalist Party. These rankings are unsurprising,
as those parties are the three main political parties in the Australian
House of Representatives\textsuperscript{16}.}

@@

To enhance the usability of our database, we added a \texttt{uniqueID}
variable to each file. This serves as a unique identifier for each
speaking MP, and comes from the \texttt{uniqueID} variable present
within data from both the \texttt{AustralianPoliticians} and
\texttt{AustralianElections} R packages\textsuperscript{6,17}. By
including this variable, one can readily integrate our data records with
those available in these two packages. \textbf{Similarly, we added the
\texttt{partyfacts\_id} variable to our data which allows users to link
our data to external political party data sources with this unique
identifier.}

Further, the \texttt{name.id} variable found in each file is another
unique identifier for each MP. This variable was parsed directly from
the Hansard XML files, and can be found in the Australian Parliamentary
Handbook. As such, our data records can be integrated with those from
the \texttt{ausPH} package which provides datasets for contents of the
Australian Parliamentary Handbook\textsuperscript{5}. This will allow
for convenient extraction of further details on each MP in a tidy, ready
to analyze format.

>>>>

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Digitization of the Australian Parliamentary Debates, 1998-2022},
  pdfauthor={Lindsay Katz; Rohan Alexander},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{July 6, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, enhanced, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, \textbf{formally
known as Hansard\textsuperscript{1},} plays a fundamental role in
capturing the history of political proceedings and facilitating the
exploration of valuable research questions. Originating in the British
parliament, the production of Hansard became tradition in many other
Commonwealth countries, such as Canada and Australia\textsuperscript{2}.
Given the content and magnitude of these records, they have
significance, particularly in the context of political science research.
In the case of Canada, the Hansard has been digitized for 1901 to
2019\textsuperscript{3}. Having a digitized version of Hansard enables
researchers to conduct text analysis and statistical modelling.
Following the lead of that project, in this paper we introduce a similar
database for Australia. This is composed of individual datasets for each
sitting day in the House of Representatives from 1998 to 2022,
containing details on everything said in parliament in a form that can
be readily used by researchers. With the development of tools for
large-scale text analysis, this database will serve as a resource for
understanding political behaviour in Australia over time.

\textbf{There are a wide variety of potential applications of this
database. For instance, within Australia there is considerable concern
that there has been a decline in the `quality' of public policy debate
(however that might be defined). Our dataset could be used to look at
whether it is really getting worse in particular ways, and if so, why.
We might also be interested in whether particular sub-populations are
appropriately represented in what is talked about in parliament. For
instance, there is often concern that regional areas are overlooked
compared with metropolitan areas. Again, our database could be used to
examine whether this has changed over time. We have developed our
database in such a way that it could be linked with similar databases
from other countries which would enable comparative analysis. For
instance, we may be interested in how the policy focus of a parliament
changes given various global events such as pandemics or wars. An
international linkage provides a comparison case where domestic issues
are different while international ones are common. As an example of
enabling this linkage this we have included partyfacts IDs in our
database. This should make it possible to link our database with other
large parliamentary speech collection projects, such as
ParlaMint\textsuperscript{4}, ParlSpeech\textsuperscript{5},
ParlEE\textsuperscript{6}, and MAPLE\textsuperscript{7}.}

The Australian House of Representatives `the House' performs a number of
crucial governmental functions, such as creating new laws and overseeing
government expenditure\textsuperscript{8, ch.~1}. Politicians in the
House are referred to as Members of Parliament (MPs). The House operates
under a parallel chamber setup, meaning there are two debate venues
where proceedings take place: the Chamber, and the Federation Chamber.
Sittings of the House follow a predefined order of business, regulated
by procedural rules called standing orders\textsuperscript{8, ch.~8}. A
typical sitting day in the Chamber has a number of scheduled proceedings
including debates on government business, 90 second member statements,
and Question Time\textsuperscript{8, ch.~8}. The Federation Chamber was
created in 1994 as a subordinate debate venue of the Chamber. This
allows for better time management of House business as its proceedings
occur simultaneously with those of the Chamber\textsuperscript{8,
ch.~21}. Sittings in the Federation Chamber are different to those of
the Chamber in terms of their order of business and scope of discussion.
Business matters discussed in the Federation Chamber are limited largely
to intermediate stages of bill development, and the business of private
Members\textsuperscript{8, ch.~21}. It is the recording and compilation
of these proceedings on which Hansard is based, and it is essentially,
but not entirely, verbatim.

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not easily accessible for large scale analysis. To
this point, various researchers have had to create their own databases
of usable, complete data based on content from the Australian Parliament
website. For instance, an online, easy to read database of Hansard from
1901 to 1980 using the XML files has been created\textsuperscript{9}.
These data can be navigated by year, parliament, people, and
bills\textsuperscript{9}. To make the Australian Parliamentary Handbook
more accessible, an \texttt{R} package which includes data on all MPs
from 1945 to 2019 has been created\textsuperscript{10}. Further, there
is the \texttt{AustralianPoliticians} \texttt{R} package, which contains
several datasets related to the political and biographical information
of Australian federal politicians who were active between 1901 and
2021\textsuperscript{11}. \textbf{And finally, there has been
examination of speech and MP level data between 1990 and 2019 in
Australia\textsuperscript{12}. Like us they scrape the Hansard record
and link it with biographical data. They key difference is that our
focus is on the database itself, while are focused on using a database
constructed from the same source to answer a particular question about
speaker time. This different focus leads to different emphasis and
approaches.}

Many papers exist which use components of Australian Hansard to explore
various research topics. For example, the Hansard has been used to
investigate occurrences of unparliamentary comments by MPs, where the
Speaker tells that MP to withdraw their remark\textsuperscript{13}.
Question Time data from Hansard transcripts during February and March of
2003 has been used to investigate resistance of politicians in answering
questions about Iraq\textsuperscript{14}. Hansard has been used to
quantify political prominence by investigating strategic mentions of
interest groups by elected officials\textsuperscript{15}. Finally, a
dataset of the Australian Hansard has been constructed and then used to
analyze the effect of elections and changes in Prime Ministers upon
topics mentioned in parliament\textsuperscript{16}. This was created
with the static PDF versions of Hansard, using OCR to digitize these
files into text which is suitable for analysis. This means there are
considerable digitization errors especially in the first half of the
dataset.

@@

The approach to parsing contents of an XML document depends on its tree
structure. As such, to create this database, we started by looking at a
single Hansard XML transcript from 2019. Doing so enabled us to identify
the various components of interest in the document, and how each one can
be parsed according to its corresponding structural form. Parsing was
performed in \texttt{R} using the \texttt{XML} and \texttt{xml2}
packages\textsuperscript{17,18}. Focusing on one transcript also allowed
us to ensure that all key components of the transcript were parsed and
captured in as much detail as possible. The typical form of a Hansard
XML transcript is summarized in the nested list below. This provides an
overview, but does not contain every possible nested element that may be
found in a Hansard XML.

@@

The next step was to further develop our script to produce tidy data
sets, as defined and introduced by\textsuperscript{19}. These contain
all parsed text elements, where each statement is separated onto its own
row with details about the MP who is speaking, and rows are maintained
in chronological order. This first involved correcting the variable
classes and adding several indicator variables to differentiate where
statements came from, such as Chamber versus Federation Chamber or
\texttt{\textless{}subdebate.1\textgreater{}} versus
\texttt{\textless{}subdebate.2\textgreater{}}. The next key task stemmed
from the fact that the raw text data were not separated by each
statement when parsed. In other words, any interjections, comments made
by the Speaker or Deputy Speaker and continuations within an individual
speech were all parsed together as a single string. As such, the name,
name ID, electorate and party details were only provided for the person
whose turn it was to speak. There were many intricacies in the task of
splitting these speeches in a way that would be generalizable across
sitting days. Details on these are provided in
Section~\ref{sec-interject}.

@@

The need for a second script stems from the fact that when established
in 1994, the Federation Chamber was originally named the Main Committee.
The Main Committee was renamed to the Federation Chamber in
mid-2012\textsuperscript{8, ch.~21}. As a result, the child node under
which Federation Chamber proceedings are nested is named
\texttt{\textless{}maincomm.xscript\textgreater{}} in all XML files
prior to 14 August 2012. Having developed our first script based on
Hansard from recent years, all XPath expressions contain the
\texttt{\textless{}fedchamb.xscript\textgreater{}} specification. To
avoid causing issues in our first script which successfully parses about
10 years of Hansard, we created a second script where we replaced all
occurrences of \texttt{\textless{}fedchamb.xscript\textgreater{}} with
\texttt{\textless{}maincomm.xscript\textgreater{}}. After making this
modification and accounting for other small changes such as time stamp
formatting, this second script successfully parses all Hansard sitting
days from 10 May 2011 to 28 June 2012 (inclusive).

@@

A key characteristic of the Australian parliamentary system is the
ability for the executive government to be held accountable for their
decisions. One core mechanism by which this is achieved is called
Question Time. This is a period of each sitting day in the Chamber where
MPs can ask ministers two types of questions: questions in writing which
are written in advance, or questions without notice which are asked
verbally in the Chamber and are responded to in real
time\textsuperscript{20}. Questions without notice are included directly
in the \texttt{"chamber.xscript"} child node, with sub-child nodes
called \texttt{"question"} and \texttt{"answer"} to differentiate the
two. Questions in writing, however, are embedded in their own child node
called \texttt{"answers.to.questions"} at the end of the XML file.

@@

We then added an order variable to the dataset based on row number, to
keep track of the order in which everything was said. The next step was
to fill the name, name ID, electorate and party variables with the
correct data for each row. We also wanted to add the gender and unique
identifier for each individual as found in the
\texttt{AustralianPoliticians} package. To do so, we created a lookup
table, which contained the unique incomplete form in which the name was
transcribed, and the corresponding full name, name ID, electorate,
party, gender, and unique ID for that individual.
Figure~\ref{fig-lookup} provides an example of this. We used the main
dataset from the \texttt{AustralianPoliticians} package in the creation
of each lookup table\textsuperscript{11}.

@@

\textbf{Another fundamental component of parliamentary proceedings is
voting. In the House, when a question arises such as ``The question is
that the amendment be agreed to'', Members are asked to cast their vote
either in the affirmative or in the negative, and the majority of votes
as judged by the Speaker determines the outcome\textsuperscript{8}.
Further, Members can vote in an unofficial arrangement called pairs,
which ``can be used to enable a Member on one side of the House to be
absent for any votes when a Member from the other side is to be absent
at the same time or when, by agreement, a Member abstains from
voting''\textsuperscript{8}. If the result as determined by the Speaker
is challenged by more than one MP, this leads to a division of the House
in which the question is re-stated and Members must move to the left or
right of their chair depending on how they vote, so that the votes can
be re-counted and recorded\textsuperscript{8}.}

@@

Our database is available in both CSV and parquet formats. Both CSV and
parquet are open standards. We provide both because while CSVs are
commonly used and can be manually inspected, parquet files are typically
smaller and preserve class. Our database covers all sitting days of the
House of Representatives from 02 March 1998 to 08 September 2022
\textbf{where an XML transcript is available}, so there are
\textbf{1,532 individual sitting day} files for each format.
\textbf{Additionally, there is a single corpus file in both CSV and
Parquet forms containing the data from all sitting days, with a date
variable added to allow for distinction and filtering of individual
sitting days. There is also a CSV and Parquet file containing all parsed
debate topics.} All data records are available on the general-purpose
repository Zenodo, at
https://doi.org/10.5281/zenodo.7799678\textsuperscript{21}. For each
\textbf{Hansard data} file, \textbf{that is, the corpus and the
individual sitting day files}, each row contains an individual
statement, with details on the individual speaking. For general
statements transcribed as made by ``Honourable members'' for example,
these variables cannot be specified. Table~\ref{tbl-vars} provides an
overview of each variable found in the \textbf{Hansard data files in
the} database.

@@

{\centering \includegraphics[width=4.58333in,height=\textheight]{images/n_daily_speeches.png}

@@

\textbf{Next, we explored the number of unique names detected on each
sitting day disaggregated by debate venue, visualized in
Figure~\ref{fig-names}. As expected, there are generally more individual
MPs detected to be present in the Chamber proceedings in our data than
in the Federation Chamber proceedings. Further, in both venues, the
number of individuals detected per sitting day appears to have increased
since around 2008-2009, with a maximum of 116 and 87 unique names
detected for the Chamber and Federation Chamber, respectively. Across
the time frame of our data, there was a daily average of 84 unique names
detected in the Chamber, and 34 in the Federation Chamber. These
observations are in accordance with the official number of Members
belonging to the House of Representatives, which was 148 in 1998, 150 in
2001, and then increased to 151 in the 2019 general
election\textsuperscript{8}.}

@@

{\centering \includegraphics[width=4.58333in,height=\textheight]{images/n_unique_names.png}

@@

\textbf{We then computed the total number of speeches made in our
database by political party, summarized in
Table~\ref{tbl-speeches_by_party}. We found that the Australian Labor
Party made the most speeches overall, followed by the Liberal Party of
Australia, and the Nationalist Party. These rankings are unsurprising,
as those parties are the three main political parties in the Australian
House of Representatives\textsuperscript{22}.}

@@

To enhance the usability of our database, we added a \texttt{uniqueID}
variable to each file. This serves as a unique identifier for each
speaking MP, and comes from the \texttt{uniqueID} variable present
within data from both the \texttt{AustralianPoliticians} and
\texttt{AustralianElections} R packages\textsuperscript{11,23}. By
including this variable, one can readily integrate our data records with
those available in these two packages. \textbf{Similarly, we added the
\texttt{partyfacts\_id} variable to our data which allows users to link
our data to external political party data sources with this unique
identifier.}

Further, the \texttt{name.id} variable found in each file is another
unique identifier for each MP. This variable was parsed directly from
the Hansard XML files, and can be found in the Australian Parliamentary
Handbook. As such, our data records can be integrated with those from
the \texttt{ausPH} package which provides datasets for contents of the
Australian Parliamentary Handbook\textsuperscript{10}. This will allow
for convenient extraction of further details on each MP in a tidy, ready
to analyze format.
